19Q1

### 2019-03-12 19Q1.Rmd
update 19Q1 rmd

# CCLE
## Note that ActArea is NOT an AUC value
ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
ccle_filt$source_histology <- ifelse(as.character(ccle_filt$source_histology) == "", NA, as.character(ccle_filt$source_histology))
ccle_filt$compound_name <- toupper(ccle_filt$Compound)
colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
ccle_auc_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
ccle_auc_long$source <- "CCLE"
ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ccle_auc[, 5:ncol(ccle_auc)] <- ccle_auc[, 5:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

# CTRP
## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
ctrp_auc_long$source <- "CTRP"
ctrp_auc_long$sample_id <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x = GDSC
gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
gdsc_auc_long$source <- "GDSC"
gdsc_auc_long$sample_id <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
gdsc_auc[, 5:ncol(gdsc_auc)] <- gdsc_auc[, 5:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

>>>>

# CCLE
## Note that ActArea is NOT an AUC value
ccle_filt <- ccle[, c("CCLE Cell Line Name", "ActArea", "Compound")]
ccle_filt$source_ccl_name <- sapply(strsplit(as.character(ccle_filt$`CCLE Cell Line Name`), split = "_"), function(x) x[1])
ccle_filt$source_histology <- tolower(gsub("^[a-z0-9]*_", "", ccle_filt$`CCLE Cell Line Name`, ignore.case = TRUE))
# FIX CCL NAMES BEING PUT INTO HISTOLOGY COLUMN
# ccle_filt$source_histology <- ifelse(grepl("^[a-z0-9]*", ccle_filt$source_histology), NA, ccle_filt$source_histology)
ccle_filt$source_histology <- ifelse(as.character(ccle_filt$source_histology) == "", NA, as.character(ccle_filt$source_histology))
ccle_filt$compound_name <- toupper(ccle_filt$Compound)
colnames(ccle_filt)[colnames(ccle_filt) == "ActArea"] <- "AUC"
ccle_auc_long <- select(ccle_filt, source_ccl_name, source_histology, compound_name, AUC)
ccle_auc_long$source <- "CCLE"
ccle_auc_long$sample_id <- with(ccle_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ccle_auc <- dcast(ccle_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ccle_auc[, 5:ncol(ccle_auc)] <- ccle_auc[, 5:ncol(ccle_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

# CTRP
## area_under_curve: integrated area under the sigmoid-fit concentration-response curve
ctrp_filt <- ctrp[, c("experiment_id", "area_under_curve", "master_cpd_id")]
ctrp_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_cell_line_20190306.txt"), master_ccl_id, ccl_name, ccle_primary_site)
ctrp_meta_exp <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_experiment_20190306.txt"), experiment_id, master_ccl_id)
ctrp_meta_cpd <- select(read.delim("./data_munging/pharmacogenomics_raw_files/CTRP_v20.meta.per_compound_20190306.txt"), master_cpd_id, cpd_name)
ctrp_keep <- merge(merge(ctrp_meta_ccl, ctrp_meta_exp, by = "master_ccl_id", all = TRUE), merge(ctrp_meta_cpd, ctrp_filt, by = "master_cpd_id", all = TRUE), by = "experiment_id", all = TRUE)
ctrp_keep$cpd_name <- toupper(ctrp_keep$cpd_name)
ctrp_keep$ccle_primary_site <- ifelse(as.character(ctrp_keep$ccle_primary_site) == "", NA, as.character(ctrp_keep$ccle_primary_site))
ctrp_auc_long <- select(ctrp_keep, ccl_name, ccle_primary_site, cpd_name, area_under_curve)
colnames(ctrp_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
ctrp_auc_long$source <- "CTRP"
ctrp_auc_long$sample_id <- with(ctrp_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
ctrp_auc <- dcast(ctrp_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
ctrp_auc[, 5:ncol(ctrp_auc)] <- ctrp_auc[, 5:ncol(ctrp_auc)] %>% replace_with_na_all(condition = ~.x == 10000)

# GDSC
gdsc_meta_ccl <- select(read.delim("./data_munging/pharmacogenomics_raw_files/GDSC_Cell_Lines_Details.csv", sep = ","), Line, Site)
gdsc_filt <- gdsc[, c("CELL_LINE_NAME", "DRUG_NAME", "AUC")]
gdsc_filt$DRUG_NAME <- toupper(gdsc_filt$DRUG_NAME)
colnames(gdsc_filt)[colnames(gdsc_filt) ==  "CELL_LINE_NAME"] <- "Line"
gdsc_filt <- merge(gdsc_filt, gdsc_meta_ccl, by = "Line", all = TRUE)
gdsc_auc_long <- select(gdsc_filt, Line, Site, DRUG_NAME, AUC)
colnames(gdsc_auc_long) <- c("source_ccl_name", "source_histology", "compound_name", "AUC")
gdsc_auc_long$source <- "GDSC"
gdsc_auc_long$sample_id <- with(gdsc_auc_long, paste(source, source_ccl_name, source_histology, sep = "_"))
gdsc_auc <- dcast(gdsc_auc_long, source + source_ccl_name + source_histology + sample_id ~ compound_name, value.var = "AUC", fun.aggregate = mean, fill = 10000)
gdsc_auc[, 5:ncol(gdsc_auc)] <- gdsc_auc[, 5:ncol(gdsc_auc)] %>% replace_with_na_all(condition = ~.x == 10000)
